---
title: "2022 01analysis-for-smart devices-data"
author: "abdelrahman Ashraf"
date: "2/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tibble)
library(skimr)
library(janitor)
library(ggplot2)
library(palmerpenguins)
library(dplyr)
library(sqldf)
sleep_day <- read.csv('sleepDay_merged.csv')
daily_activity <- read.csv('dailyActivity_merged.csv')

```

## summary for analysis watches data

objective:
analyze smart device usage data in order 
to gain insight into how consumers use smart
devices

firstly we have two  data from third-party sources:
  1- sleep_Day
  2- daily_activity

so we should merge these data to find out relationships between  differents activities  
  so we start with this code

You can also embed plots, for example:
```{r }
combined_data <- merge(sleep_day, daily_activity, by = "Id")
ws <- combined_data
n_distinct(combined_data$Id)

```

so we observe we have 24 id related with two data 

## what ralationship between fairly active minutes and burn calories?

```{r echo=TRUE}
ggplot(data = combined_data, aes(y= Calories,x=FairlyActiveMinutes))+
  geom_point()+
  geom_smooth(method = 'gam',formula = y~s(x))

```

so we find most observations between 0 and 50 minutes
   with average calories 2316.836 and
   11508 observations from origin 12441
   so every body have low fairly active minutes 
   who have high potiontial to use smart devices 

##  so let us move to find relation between sleeping and burn calories


```{r , echo=TRUE}

ggplot(data = ws, aes(x= TotalMinutesAsleep,y=Calories))+
  geom_jitter()+
  geom_smooth(method = 'gam',formula = y~s(x))
```
```{r , echo=FALSE}

we <- ws%>%
  arrange(Calories)%>%
  filter(Calories > 0)%>%
  filter(TotalMinutesAsleep > 300, TotalMinutesAsleep < 575)
midle_specifies<- c("mostPeople_with_minutes_sleep",
    nrow(we),
    mean(we$Calories),
    median(we$Calories),
    max(we$Calories))
##}
less_300_min <- ws%>%
  arrange(Calories)%>%
  filter(Calories > 0)%>%
  filter(TotalMinutesAsleep < 300)
##summary
less_specifies<- c("less_minutes_sleep",
    nrow(less_300_min),
    mean(less_300_min$Calories),
    median(less_300_min$Calories),
    max(less_300_min$Calories))
larger_575_min <- ws%>%
  arrange(Calories)%>%
  filter(Calories > 0)%>%
  filter(TotalMinutesAsleep > 575)
pivot_we <- summary(we)

larg_specifies<- c("larger_minutes_sleep",
    nrow(larger_575_min),
    mean(larger_575_min$Calories),
    median(larger_575_min$Calories),
    max(larger_575_min$Calories))
summar <- data.frame(c("name","count_of_records","averageCalories","medianCalories","maximamCalories"),larg_specifies,less_specifies,midle_specifies)
summur <- as.data.frame(summar)
```

```{r , echo=TRUE}

head(summar)

```
so

### 1- we find most peoble were burning calories 

   in peroid between 300 and 575 minutes sleeping
   with average 2378 and with 10235 observations 
   from origin 12441
   with maximam calories 4900
   
### 2- the less peoble were burning calories 

   in peroid larger than 575 minuite sleeping
   with average 2218 and with 672 observations 
   from origin 12441
   but they peoble were still high calories but thier potiontial to burn calories very lower
   
###  3- the  peoble were burning calories 

   in peroid lower than 300 minuite sleeping
   with less average 2083 by comparing another peroids
   and with 1509 observations 
   from origin 12441
   with maximam calories 4552
   
## so let us move to another chart to explore relation between rate between sedantry minutes and burning calories

```{r ,echo=TRUE}
ggplot(data = ws, aes(x= SedentaryMinutes , y=Calories))+
  geom_jitter()+
  geom_smooth(method = 'gam',formula = y~s(x))

```

so we find most peoble burning calories those were who had from 500 to 1000 minutes in the day  but those peoble were  who had less than 500 it couldnt burning calories and there are potintial with the peoble were who had larger than 1000 Sedentary minutes

##  let us move to another chart to find out relation between total steps and burning calories

```{r ,echo=TRUE}
ggplot(data = ws, aes(x= TotalSteps,y=Calories))+
  geom_jitter()+
  geom_smooth(method = 'gam',formula = y~s(x))

```

we found postive relation between total steps's every person and burning calories  but the peoble who have more steps they less when the rate of steps larg


##  Recommendations


* Attract people who were had from 0 to 50  Activate minutes in the every day and tell because they had a big chance to use smart device

* Attract people who were had from 325 to 675 sleeping minutes in the every day

* Attract people who were had from 500 to 1250 free minutes in every day

* Attract people who were had 0 to 15000 total steps in every day



